%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Developer CV
% LaTeX Template
% Version 1.0 (28/1/19)
%
% This template originates from:
% http://www.LaTeXTemplates.com
%
% Authors:
% Jan Vorisek (jan@vorisek.me)
% Based on a template by Jan Küster (info@jankuester.com)
% Modified for LaTeX Templates by Vel (vel@LaTeXTemplates.com)
%
% License:
% The MIT License (see included LICENSE file)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[9pt]{developercv} % Default font size, values from 8-12pt are recommended
\usepackage{amssymb}
%----------------------------------------------------------------------------------------

\definecolor{bgcolor}{rgb}{0.85,0.85,0.85}
\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\newcommand{\header}[1]{\begin{tikzpicture}[remember picture,overlay]
    \node[yshift=-4cm] at (current page.north west)
      {\begin{tikzpicture}[remember picture, overlay]
        \draw[fill=gray,line width=0pt] (0,0) rectangle
          (\paperwidth,4cm);
        \node[anchor=east,xshift=0.95\paperwidth,rectangle,
              rounded corners=20pt,inner sep=11pt, yshift=1.65cm,
              fill=gray]
              {#1};
       \end{tikzpicture}
      };
   \end{tikzpicture}
\vspace{2.5cm}
  }

\header{

\vspace{12pt}
\begin{minipage}[t]{0.44\textwidth} % 45% of the page width for name
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% If your name is very short, use just one of the lines below
	% If your name is very long, reduce the font size or make the minipage wider and reduce the others proportionately

	
	\textcolor{white}{\HUGE\textbf{\MakeUppercase{R. Chris}}} % First name
	\vspace{-6pt}

	\HUGE\textbf{\MakeUppercase{Ehemann}}
%	\Huge\textbf{\MakeUppercase{Ehemann}} % Last name

	\vspace{-20pt}

	{\Large Ph.D., Data Scientist} % Career or current job title

\end{minipage}\hfill
\begin{minipage}[t]{0.28\textwidth} % 27.5% of the page width for the first row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
	% Other icons can be found by referring to fontawesome.pdf (supplied with the template) and using the word after \fa in the command for the icon you want
	\icon{MapMarker}{16}{New Albany, OH 43054}\\
	\icon{Phone}{16}{+1 931 588 1446}\\
	\icon{At}{16}{\href{mailto:rcehemann@gmail.com}{rcehemann@gmail.com}}\\	


\end{minipage}
\begin{minipage}[t]{0.28\textwidth} % 27.5% of the page width for the second row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
	% Other icons can be found by referring to fontawesome.pdf (supplied with the template) and using the word after \fa in the command for the icon you want
	\icon{Laptop}{16}{\href{http://ehemannrc.info}{ehemannrc.info}}\\	
	\icon{Linkedin}{16}{\href{https://www.linkedin.com/in/robert-c-ehemann/}{R.C. Ehemann}}\\
	\icon{Github}{16}{\href{https://github.com/rcehemann}{github.com/rcehemann}}\\

\end{minipage}

}
%\vspace{0.5cm}

%----------------------------------------------------------------------------------------
%	INTRODUCTION, SKILLS AND TECHNOLOGIES
%----------------------------------------------------------------------------------------


\begin{minipage}[t]{0.5\textwidth}
	%\vspace{-\baselineskip} % Required for vertically aligning minipages
	\begin{minipage}[t]{\textwidth} % 40% of the page width for the introduction text	
	\Large Driven, creative, and charismatic\\computational problem-solver\\ % Dummy text
	\end{minipage}

	\vspace{-\baselineskip}
	\cvsect{Gears}{Tools \& Techniques}

	\begin{minipage}[t]{\textwidth}
%	\vspace{1pt}
	\foreach \tool in {Jupyter,Pandas,Scikit-learn,Keras,PyMC3,Statsmodels,XGBoost,ARIMA,GARCH,Flask,Dash,Plotly,Seaborn,MPL,nonlinear programming,evolutionary programming}{\tech{\tool}}
	\end{minipage}
\end{minipage}
\hfill % Whitespace between
\begin{minipage}[t]{0.45\textwidth} % 50% of the page for the skills bar chart
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	\vspace{0.5cm}
	\begin{barchart}{5.5}
		\baritem{Python}{95}
		\baritem{bash}{75}
		\baritem{Julia}{55}
		\baritem{JS/HTML}{45}
		\baritem{SQL}{45}
		\baritem{Git}{55}
		\baritem{R}{25}

	\end{barchart}
\end{minipage}

%\begin{center}
%	\bubbles{6/optimization, 0/, 5/time series, 0/, 4/full-stack, 0/, 5/visualization, 0/, 6/communication}
%\end{center}

%----------------------------------------------------------------------------------------
%	EXPERIENCE
%----------------------------------------------------------------------------------------

\cvsect{Briefcase}{Experience}

\begin{entrylist}
	\entry
		{May 2019 --\\ Present}
		{Manufacturing Data Scientist}
		{Owens Corning}
		{Primary data scientist in Owens Corning's Advanced Manufacturing organization. Supported organizational objectives of productivity and cost take-out by building predictive models of manufacturing processes, partnering with SMEs to test "tribal knowledge" with big data and visualization, performing numerous statistical analyses and mentoring other analytics practitioners. As a corporate resource, also provided analytics support to product development and marketing teams throughout OC.\\ \foreach \tool in {Python,Julia,SQL}{\tech{\tool}}}
	\entry
		{Jan 2018 --\\ May 2019}
		{Data Scientist}
		{Owens Corning}
		{Formative member of a data science team in Owens Corning Science \& Technology. Focused on accelerating product development by building predictive and prescriptive applications for product performance/optimization and leveraging large historical datasets for statistical analyses published and/or presented internally. Led three interns while managing multiple projects with competing priorities.\\ \foreach \tool in {Python,JavaScript}{\tech{\tool}}}
	\entry
		{2010 \& 2011\\\footnotesize{June -- August}}
		{Intern, Atomic \& Molecular Physics}
		{Oak Ridge National Laboratory}
		{Leveraged world-class supercomputing resources to model the interaction of hydrogen atoms with carbon nano-structures using classical and semi-classical simulation techniques.\\ \foreach \tool in {HPC,bash,Fortran}{\tech{\tool}}}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\cvsect{GraduationCap}{Education}

\begin{entrylist}
	\entry
		{December 2018}
		{Ph.D.}
		{The Ohio State University}
		{Physics, 4.0, {\emph{Specialization: Computational materials physics}} \\ Utilized high-performance computing to optimize physical models of atomic-level interactions in metals using evolutionary algorithms.\\ \foreach \tool in {Python,bash,C++,HPC}{\tech{\tool}}}
	\entry
		{May 2015}
		{Master of Science}
		{The Ohio State University}
		{Physics, 4.0}
	\entry
		{May 2012}
		{Bachelor of Science}
		{Middle Tennessee State University}
		{Physics and Mathematics, 3.9}
\end{entrylist}
\clearpage
%----------------------------------------------------------------------------------------
%	ADDITIONAL INFORMATION
%----------------------------------------------------------------------------------------

\cvsect{FileText}{Publications}
\begin{entrylist}
	\entry
		{}
		{}
		{}
		{%
\vspace{-2\baselineskip}
\renewcommand{\labelitemi}{\textcolor{gray}{$\blacksquare$}}
\begin{itemize}
\setlength{\itemindent}{-1cm}
\item Two Trade Secrets, 2019.
\item Using Analytics to Stay Ahead of the Curve in B2B Markets. C. Skinner and R. C. Ehemann, \emph{2018 BGSU Business Anallytics Symposium} (2018).
\item Force-matched interatomic potentials for tungsten and titanium-niobium. The Ohio State University, December 2017.
\item Force-matched empirical potential for martensitic transitions and plastic deformation in Ti-Nb alloys. R. C. Ehemann and J. W. Wilkins. {\emph{Physical Review B}} {\bf{96}}, 184105 (2017)
\item {\emph{Ab initio}} based empirical potential applied to tungsten at high pressure. R. C. Ehemann, J. W. Nicklas, H. Park and J. W. Wilkins. {\emph{Physical Review B}} {\bf{95}}, 184101 (2017)
\item Detection of hydrogen using graphene. R. C. Ehemann, P. S. Krstic, J. Dadras, P. R. Kent and J. Jakowski. {\emph{Nanoscale Research Letters}} {\bf{7}}, 198 (2012)
\end{itemize}}
\end{entrylist}

\cvsect{Commenting}{Presentations}
\begin{entrylist}
	\entry{}{}{}{
\vspace{-2\baselineskip}
\renewcommand{\labelitemi}{\textcolor{gray}{$\blacksquare$}}
\begin{itemize}
	\setlength{\itemindent}{-1cm}
	\item \emph{Artificial Intelligence and Machine Learning: Theory and Application in Owens Corning S\&T}, Owens Corning S\&T Tech Talk, April and May 2019. 
	\item \emph{It's a Bird, It's a Blade, it's Super-H!}, Poster (co-author), Owens Corning Science \& Technology Poster Session, 2018.  Awarded best poster.
	\item \emph{Innovating Innovation}, Poster, Owens Corning Science \& Technology Poster Session, 2018.
	\item \emph{A Novel Empirical Potential for Modeling Martensitic Transformations in Ti-Nb Alloys}, Poster, OSU Materials Week 2016. Awarded best poster.
	\item \emph{Atomistic Modeling of Ti-Nb Alloys}, Poster, Ohio Supercomputing Center Statewide Users Group Meeting 2015. Awarded best poster.
	\item \emph{Toward a Versatile Molecular Dynamics Potential for the Ti-Nb Alloy System}, Poster, OSU Materials Week 2015.
\end{itemize}}
\end{entrylist}

\cvsect{Star}{Awards \& Honors}
\begin{entrylist}
	\entry{}{}{}{
\vspace{-2\baselineskip}
\renewcommand{\labelitemi}{\textcolor{gray}{$\blacksquare$}}
\begin{itemize}
	\setlength{\itemindent}{-1cm}
 \item Slater Innovation Award, Owens Corning Science \& Technology, 2018. Awarded for the development of a high-impact predictive model
 \item Trumbull Asphalt Breakthrough Award, Owens Corning, 2018.
 \item Winner, Owens Corning Science \& Technology Poster Session, 2018
 \item University Fellowship, The Ohio State University Graduate School, 2012--2016 
 \item Fowler Fellowship, The Ohio State University Department of Physics, 2012--2014 
 \item Barry M. Goldwater Scholarship, Barry Goldwater Scholarship \& Excellence in Education Foundation, 2011--2012
\end{itemize}}
\end{entrylist}


%----------------------------------------------------------------------------------------

\end{document}
